Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2020-01-21 acks.tex
Revisions

\chapter{Acknowledgments}
Writing a PhD thesis is a significant challenge, both professionally and
personally; in a sense, it's a solitary challenge, but in fact I've had so much
help from so many, both in the research and in the personal growth that led me
here. In fact, this page might have been the hardest to write.

@@

Most importantly, thanks to my late mother Rosalia, who sadly passed near the end of my
PhD. I've struggled to thank her properly in this thesis, but I just can't; I'll
just say I'm thankful for all she did for me, and she's behind everything I am.

@@

>>>>

\chapter{Acknowledgments}
Writing a PhD thesis is a significant challenge, both professionally and
personally; in a sense, it's a solitary challenge, but in fact I've had so much
help from so many, both in the research and in the personal growth that led me
here. In fact, this page was the hardest to write, because I knew my words could
not do justice to the task.

@@

Most importantly, thanks to my late mother Rosalia, who sadly passed near the end of my
PhD. I've struggled to thank her properly in this thesis, but I just can't; I'll
just say I'm thankful for all she did for me, and that she's behind everything I
am.

@@

In sum, to all of you, \emph{thank you}: I couldn't have done this without each
of you.
